background points - is more better?

### 2018-12-05 src/background_points_no_check.Rmd
3d plot test

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
The "include=FALSE" supresses the package installation text appearing in the document...
```{r pre-install packages, include=FALSE}
packages <- c("ncdf4", "raster", "ggplot2") 
source("../src/ipak.R")
ipak(packages)
```

@@

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
The "include=FALSE" supresses the package installation text appearing in the document...
```{r pre-install packages, include=FALSE}
packages <- c("ncdf4", "raster", "ggplot2", "plotly") 
source("../src/ipak.R")
ipak(packages)
```

@@

# 3d plot background points

```{r}
bck2014_06_3d <- plot_ly(x= testbk100002014$longitude_, y = testbk100002014$latitude_m, z = testbk100002014$depthlayerno)
```
